Supporting Information : The importance of a complete description of dependence between variables for ecology and related fields

### 2019-05-06 Paper.Rmd
presentation format modified

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{(A-F, I, J) Bivariate datasets showing diverse relationships between 
variables; many of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. Panels C and E (respectively, D and F) were 
obtained from A (respectively, B) via monotonic functions that transformed the 
standard-normal marginal distributions of A and B to gamma (C, D) or 
uniform (E, F) marginals (details in Appendix \ref{SM-pedagog1_details}). (G, H) Contours 
of log-scale density functions of Clayton (G) and survival-Clayton 
(H) copulas with parameter 5 (see section on methods for Q1). (I,J) Reflections
of E, F, respectively, about a vertical axis. Subscripts h and v 
stand for "horizontal" and "vertical". \label{fig_cop_pedag1}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal (N) copula with parameter $0.8$ and the Frank (F) copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton (C) and  
survival-Clayton (SC) copulas with parameter 5. Figs \ref{SM-figped_N}-\ref{SM-figped_SBB8}
have visualizations of all the copulas we used.\label{fig_cop_pedag3}}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=6.5in]{./Results/BivarDataPlot.pdf}
\caption{Upper panels show raw data plots for (A) $\log_{10}$(soil C) and $\log_{10}$(soil N) data, (B) $\log_{10}$(basal metabolic rate (BMR)) vs. $\log_{10}$(body mass) 
for birds, (C) the same for mammals, and (D) above-ground plant biomass vs. Shannon's index \textit{(H)} from Cedar Creek. Bottom panels show the corresponding copula plots. See text for units used in upper panels. \label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}

@@

<!--para on how likely one is to get copula structure via the Moran mechanism-->
Our Moran-like mechanism for copula structure and tail dependence seems likely to
operate commonly, because Moran effects are common [@Liebhold2004], and 
non-N and tail-dependent copula structures are often found in 
environmental variables. 
If large meteorological events are 
also spatially widespread, then
one would expect environmental variables associated with these events to take extreme
values simultaneously across large spatial areas, producing tail dependence in measurements
made through time at different locations. Non-extreme values, not associated with extreme, 
spatially extensive weather events, may
be more associated with local phenomena, and therefore 
less prone to being correlated across large areas.
For instance, @Serinaldi2008 examined the spatial dependence 
of rainfall observations in Central Italy. G or Student 2-copulas 
were possible candidates for modelling dependence, and 
neither of these is an N copula.
A long-term study (1950–2014) in the Loess Plateau of China [@She2018]
showed that a G copula (which has upper tail dependence) could effectively model 
the spatial dependence of drought variables in the study area.
Bivariate copula analysis was also used in forecasting the 
co-occurrence of extreme events (flood or drought) 
over the North Sikkim Himalayas, India, using spatial data sets [@Goswami2018].

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig1.pdf}
\caption{(A-F, I, J) Bivariate datasets showing diverse relationships between 
variables; many of these datasets nevertheless have the same Pearson (P)
or Spearman (S) correlation coefficients. Panels C and E (respectively, D and F) were 
obtained from A (respectively, B) via monotonic functions that transformed the 
standard-normal marginal distributions of A and B to gamma (C, D) or 
uniform (E, F) marginals (details in Appendix \ref{SM-pedagog1_details}). (G, H) Contours 
of log-scale density functions of Clayton (G) and survival-Clayton 
(H) copulas with parameter 5 (see section on methods for Q1). (I,J) Reflections
of E, F, respectively, about a vertical axis. Subscripts h and v 
stand for "horizontal" and "vertical". \label{fig_cop_pedag1}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=3.5in]{./Results/PedagogFig3.pdf}
\caption{Log-transformed pdfs (A, C) and samples from (B, D) example copulas.
Shown are the normal (N) copula with parameter $0.8$ and the Frank (F) copula with 
parameter $10$. See also Fig. \ref{fig_cop_pedag1}E-H for the Clayton (C) and  
survival-Clayton (SC) copulas with parameter 5. Figs \ref{SM-figped_N}-\ref{SM-figped_SBB8}
have visualizations of all the copulas we used.\label{fig_cop_pedag3}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6.5in]{./Results/BivarDataPlot.pdf}
\caption{Upper panels show raw data plots for (A) $\log_{10}$(soil C) and $\log_{10}$(soil N) data, (B) $\log_{10}$(basal metabolic rate (BMR)) vs. $\log_{10}$(body mass) 
for birds, (C) the same for mammals, and (D) above-ground plant biomass vs. Shannon's index \textit{(H)} from Cedar Creek. Bottom panels show the corresponding copula plots. See text for units used in upper panels. \label{fig_biv_multi_raw_cop}}
\end{center}
\end{figure}

@@

<!--para on how likely one is to get copula structure via the Moran mechanism-->
Our Moran-like mechanism for copula structure and tail dependence seems likely to
operate commonly, because Moran effects are common [@Liebhold2004], and 
non-N and tail-dependent copula structures are often found in 
environmental variables. 
If large meteorological events are 
also spatially widespread, then
one would expect environmental variables associated with these events to take extreme
values simultaneously across large spatial areas, producing tail dependence in measurements
made through time at different locations. Non-extreme values, not associated with extreme, 
spatially extensive weather events, may
be more associated with local phenomena, and therefore 
less prone to being correlated across large areas.
For instance, @Serinaldi2008 examined the spatial dependence 
of rainfall observations in Central Italy. G or Student 2-copulas 
were possible candidates for modelling dependence, and 
neither of these is an N copula.
A long-term study (1950–2014) in the Loess Plateau of China [@She2018]
showed that a G copula (which has upper tail dependence) could effectively model 
the spatial dependence of drought variables in the study area.
Bivariate copula analysis was also used in forecasting the 
co-occurrence of extreme events (flood or drought) 
over the North Sikkim Himalayas, India, using spatial datasets [@Goswami2018].

### 2019-05-06 SupportingInformation.Rmd
finished a round of editing the main text, we are now within Ecol Lett length limits
presentation format modified

\begin{figure}
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 copula (see section on methods for Q1) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (methods for Q1), but the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column.\label{fig_cop_pedag}}
\end{center}
\end{figure}

@@

<!--Do the model selection for methane flux data and then showing results in Tables-->
```{r RES_methane, echo=F, cache=T, results="hide", cache.extra=list(seed,methane_data,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

@@

<!--table for Best-fitting copulas, methane flux data-->
```{r tab_methane_bestcop, echo=F, results="markup"}
knitr::kable(RES_methane$info_ord_copname[,,1], #longtable=T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, methane flux data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for methane flux data. See methods for Q1 for copula abbreviations. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_methane_bestcop}",
             booktabs=TRUE
             )
```

<!--table for AIC-weights of best-fitting copulas, methane flux data-->
```{r tab_methane_AICw,echo=F,results="markup"}
h<-RES_methane$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, best-fitting copulas, methane flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for methane flux data.\\label{tab_methane_AICw}",
             booktabs=TRUE)
```

<!--table for AIC-weights of Normal copula used for fitting, methane flux data-->
```{r tab_methane_AICw_normal,echo=F,results="markup"}
source("normal_cop_AICw.R")
h<-normal_cop_AICw_matrix(r=RES_methane)
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, N copulas, methane flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for methane flux data, for comparison with Table \\ref{tab_methane_AICw}.\\label{tab_methane_AICw_normal}",
             booktabs=TRUE)
```

<!--table for p-values from goodness of fit test (Cramer-von Mises-based test) with best-fit copula, methane flux data-->
```{r tab_methane_p_CvM,echo=F,results="markup"}
h<-RES_methane$gfc_p_CvM
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, methane flux data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for methane flux data.\\label{tab_methane_p_CvM}",
             booktabs=TRUE)
```

<!--table for p-values from goodness of fit test (Kolmogorov-Smirnov-based test) with best-fit copula, methane flux data-->
```{r tab_methane_p_KS,echo=F,results="markup"}
h<-RES_methane$gfc_p_KS
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, methane flux data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of
the goodness of fit of the lowest-AIC copula family for each pair of
locations for methane flux data.\\label{tab_methane_p_KS}",
             booktabs=TRUE)
```

<!--table for model averaged lower tail dep., methane flux data-->
```{r tab_methane_LTdep_AICw,echo=F,results="markup"}
h<-RES_methane$LTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower-tail dependence, methane flux data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for methane flux data.\\label{tab_methane_LTdep_AICw}",
             booktabs=TRUE)
```

<!--table for model averaged upper tail dep., methane flux data-->
```{r tab_methane_UTdep_AICw,echo=F,results="markup"}
h<-RES_methane$UTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Upper-tail dependence, methane flux data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for methane flux data.\\label{tab_methane_UTdep_AICw}",
             booktabs=TRUE)
```

<!--table for model averaged lower- minus upper-tail dep., methane flux data-->
```{r tab_methane_LTmUT,echo=F,results="markup"}
h<-RES_methane$LTdep_AICw-RES_methane$UTdep_AICw
h[is.nan(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower- minus upper-tail dependence, methane flux data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for methane flux data.\\label{tab_methane_LTmUT}",
             booktabs=TRUE)
```

<!--Do the main computations for nonparametric analysis of methane flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,methane_raw,latlon_methane,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Show the statistical results in a table for methane flux data-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]

@@

sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s,digits = 3,
             format = "latex",linesep = "", escape = F,align="c",
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             caption.short="Results for nonparametric statistics, methane flux data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for methane flux data.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```

@@

Asymmetry of tail dependence was also verified by our nonparametric methods for
the other multivariate datasets. For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\Ps_l-\Ps_u$ were
$(-0.085,-0.041)$ for the leaf-curling plum aphid first flight data, 
indicating greater upper-tail dependence, and consistent with
<!--***DAN: Shya, pls make above results autolink-->
the results of Table \ref{MT-tab_multivar_summary} (row 9). 
For the *Ceratium furca* abundance data, confidence intervals were
$(0.011,0.044)$, indicating greater lower-tail dependence, and again
<!--***DAN: Shya, pls make above results autolink-->
consistent with the results of Table \ref{MT-tab_multivar_summary} (row 9).
For the methane flux data, confidence intervals were 
$(-0.008,0.019)$.

@@

<!--Following chunk examine the consequence of non-Normal copula atructure on skewness using methane flux data-->
```{r skewness_methane_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

\begin{figure}
\begin{center}
\includegraphics[width=7in]{./Results/MissingDataInfluencesCopula.pdf}
\caption[Missing data can influence perceived copula structure]{Missing
data can influence perceived copula structure. Points were randomly 
removed from the upper right portion of the copula dataset pictured in A, and
then remaining values were re-ranked to make B. Thus removing data in a 
non-random fashion can influence copula structure and tail dependence. See 
Appendix \ref{sect:missingdata} for details. \label{fig:missingdata}}
\end{center}
\end{figure}

\clearpage

#  References

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 copula (see section on methods for Q1) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths (methods for Q1), but the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column.\label{fig_cop_pedag}}
\end{center}
\end{figure}

@@

<!--Do the model selection for methane-flux data and then showing results in Tables-->
```{r RES_methane, echo=F, cache=T, results="hide", cache.extra=list(seed,methane_data,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}

@@

<!--table for Best-fitting copulas, methane-flux data-->
```{r tab_methane_bestcop, echo=F, results="markup"}
knitr::kable(RES_methane$info_ord_copname[,,1], #longtable=T,
             format='latex',linesep = "",
             caption.short = "Best-fitting copulas, methane-flux data",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for methane-flux data. See methods for Q1 for copula abbreviations. Indep.=Independent. NA occurs along the diagonal because diagonal entries represent a sampling location compared to itself.\\label{tab_methane_bestcop}",
             booktabs=TRUE
             )
```

<!--table for AIC-weights of best-fitting copulas, methane-flux data-->
```{r tab_methane_AICw,echo=F,results="markup"}
h<-RES_methane$info_ord_AICw[,,1]
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, best-fitting copulas, methane-flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the best-fitting (lowest AIC) copula family for each location pair for methane-flux data.\\label{tab_methane_AICw}",
             booktabs=TRUE)
```

<!--table for AIC-weights of Normal copula used for fitting, methane-flux data-->
```{r tab_methane_AICw_normal,echo=F,results="markup"}
source("normal_cop_AICw.R")
h<-normal_cop_AICw_matrix(r=RES_methane)
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="AIC weights, N copulas, methane-flux data",
             caption = "$\\text{AIC}_{\\text{w}}$ for the N copula family for each location pair for methane-flux data, for comparison with Table \\ref{tab_methane_AICw}.\\label{tab_methane_AICw_normal}",
             booktabs=TRUE)
```

<!--table for p-values from goodness of fit test (Cramer-von Mises-based test) with best-fit copula, methane-flux data-->
```{r tab_methane_p_CvM,echo=F,results="markup"}
h<-RES_methane$gfc_p_CvM
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, methane-flux data",
             caption = "$P$-value results of a Cramer-von Mises-based test of the goodness of fit of the lowest-AIC copula family for each pair of locations for methane-flux data.\\label{tab_methane_p_CvM}",
             booktabs=TRUE)
```

<!--table for p-values from goodness of fit test (Kolmogorov-Smirnov-based test) with best-fit copula, methane-flux data-->
```{r tab_methane_p_KS,echo=F,results="markup"}
h<-RES_methane$gfc_p_KS
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Goodness of fit of best-fitting copulas, methane-flux data",
             caption = "$P$-value results of a Kolmogorov-Smirnov-based test of
the goodness of fit of the lowest-AIC copula family for each pair of
locations for methane-flux data.\\label{tab_methane_p_KS}",
             booktabs=TRUE)
```

<!--table for model averaged lower tail dep., methane-flux data-->
```{r tab_methane_LTdep_AICw,echo=F,results="markup"}
h<-RES_methane$LTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower-tail dependence, methane-flux data",
             caption = "Model-averaged lower-tail dependence statistics for each location pair for methane-flux data.\\label{tab_methane_LTdep_AICw}",
             booktabs=TRUE)
```

<!--table for model averaged upper tail dep., methane-flux data-->
```{r tab_methane_UTdep_AICw,echo=F,results="markup"}
h<-RES_methane$UTdep_AICw
h[is.infinite(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Upper-tail dependence, methane-flux data",
             caption = "Model-averaged upper-tail dependence statistics for each location pair for methane-flux data.\\label{tab_methane_UTdep_AICw}",
             booktabs=TRUE)
```

<!--table for model averaged lower- minus upper-tail dep., methane-flux data-->
```{r tab_methane_LTmUT,echo=F,results="markup"}
h<-RES_methane$LTdep_AICw-RES_methane$UTdep_AICw
h[is.nan(h)]<-NA
knitr::kable(h,
             format="latex",linesep = "",
             digits=3,
             caption.short="Lower- minus upper-tail dependence, methane-flux data",
             caption = "Model-averaged lower-tail dependence statistics minus model-averaged upper-tail dependence statistics for each location pair for methane-flux data.\\label{tab_methane_LTmUT}",
             booktabs=TRUE)
```

<!--Do the main computations for nonparametric analysis of methane-flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,methane_raw,latlon_methane,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Show the statistical results in a table for methane-flux data-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]

@@

sc<-as.data.frame(c("Spearman","Kendall","cor$_{l}$","cor$_{u}$","P$_{l}$","P$_{u}$","D$_{l}^2$","D$_{u}^2$",
                    "cor$_{l}$ - cor$_{u}$","P$_{l}$ - P$_{u}$","D$_{u}^2$ - D$_{l}^2$"))
s<-cbind(sc,s)
knitr::kable(s,digits = 3,
             format = "latex",linesep = "", escape = F,align="c",
             col.names=c("","2.5$^{th}$ quantile", "Mean", "97.5$^{th}$ quantile"),
             caption.short="Results for nonparametric statistics, methane-flux data",
             caption = "Average values of statistics across all locations pairs and confidence intervals based on spatial resampling for methane-flux data.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```

@@

Asymmetry of tail dependence was also verified by our nonparametric methods for
the other multivariate datasets. For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\Ps_l-\Ps_u$ were
$(-0.085,-0.041)$ for the leaf-curling plum aphid first flight data, 
indicating greater upper-tail dependence, and consistent with
<!--***DAN: Shya, pls make above results autolink-->
the results of Table \ref{MT-tab_multivar_summary} (row 9). 
For the *Ceratium furca* abundance data, confidence intervals were
$(0.011,0.044)$, indicating greater lower-tail dependence, and again
<!--***DAN: Shya, pls make above results autolink-->
consistent with the results of Table \ref{MT-tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
$(-0.008,0.019)$.

@@

<!--Following chunk examine the consequence of non-Normal copula atructure on skewness using methane-flux data-->
```{r skewness_methane_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7in]{./Results/MissingDataInfluencesCopula.pdf}
\caption[Missing data can influence perceived copula structure]{Missing
data can influence perceived copula structure. Points were randomly 
removed from the upper right portion of the copula dataset pictured in A, and
then remaining values were re-ranked to make B. Thus removing data in a 
non-random fashion can influence copula structure and tail dependence. See 
Appendix \ref{sect:missingdata} for details. \label{fig:missingdata}}
\end{center}
\end{figure}

# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{1pt}
\noindent
